% adapted by WS from SSR's Word document and from the 5-part series at
% https://www.overleaf.com/learn/latex/How_to_Write_a_Thesis_in_LaTeX_(Part_1):_Basic_Structure
% reviewed by MAM

\documentclass[12pt,twosided]{report}

\usepackage[titletoc]{appendix} % for adding appendix to TOC
\usepackage{biblatex} % reference management
\usepackage{geometry}  % better margins and margin control
\usepackage{graphicx}  % to include figures
\usepackage{hyperref}  % internal and external links
\usepackage[utf8]{inputenc}  % support for non-ASCII characters
\usepackage{listings}  % typset code
\usepackage{outlines}  % easy nesting of lists
\usepackage{tabularx}  % more control over table column width
\usepackage{titlesec}  % customize chapter title
\usepackage{upquote}  % prevent mishandling of single quotes in listings
\usepackage{float}
\usepackage{longtable}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{booktabs}
\usepackage{url}         % Allows line breaks in URLs



% TODO: Customize the appearance of hyperref links using \hypersetup
% See https://en.wikibooks.org/wiki/LaTeX/Hyperlinks#Customization

% Custom format of chapter title.
\titleformat{\chapter}[hang]{\bf\huge}{\thechapter.}{2pc}{}

% Separate folder for images named 'images'.
\graphicspath{ {images/} }

% Separate file for references
\addbibresource{references.bib}

% Replace with your title
\title{Public Chat Portal for AlKhidmat}

% Allow recalling document title
% from https://tex.stackexchange.com/a/15806/44301
\makeatletter\let\Title\@title\makeatother  

\begin{document}

\include{titlepage}  % title page.
\include{approval}  % approval page.

\chapter*{Dedication}
We sincerely dedicate this project to our beloved parents, who have been our greatest source of strength and support throughout our academic journey. Their constant love, endless prayers, and sacrifices have shaped us into the individuals we are today. We are truly grateful for their patience during the late nights and stressful deadlines of this final year.

We also dedicate this work to our siblings and friends for their continuous motivation and belief in our potential. A special dedication goes to our team, as this journey would not have been possible without our mutual respect and the countless hours we spent problem-solving together.

Finally, we dedicate this project to Almighty God for blessing us with the knowledge, health, and perseverance to complete this work. We are thankful for the guidance that allowed us to finish this project with purpose and dedication.

\chapter*{Acknowledgements}
Our team would like to extend our heartfelt gratitude to our supervisor and mentors at Habib University for their constant guidance and technical oversight throughout this project. Their expertise and commitment to our learning allowed us to navigate various challenges and deliver a project we are proud of.

We express our sincere thanks to the Alkhidmat Foundation Pakistan for providing us with the opportunity to work on this initiative. We are especially grateful to the domain experts and staff who shared their organizational knowledge and internal documentation, which formed the foundation of our knowledge base.

\chapter*{Abstract}
The \textbf{Alkhidmat Public Chat Portal} is an AI-powered, multi-domain organizational assistant designed to bridge communication gaps for one of Pakistan's largest non-profit organizations. Addressing the operational burden of manually handling thousands of daily inquiries, the system provides an automated solution for \textbf{donors, volunteers, and beneficiaries}. Unlike existing single-domain chatbots in Pakistan, this platform integrates a \textbf{Retrieval-Augmented Generation (RAG)} framework to provide verified, contextually accurate information across multiple sectors, including \textbf{healthcare, disaster management, blood services, and orphan care}.

The system architecture employs a five-layer structure—Presentation, Application, AI/ML, Data, and Infrastructure—supporting multilingual interaction in \textbf{English, Urdu, and Roman Urdu}. Key technical features include:
\begin{itemize}
    \item \textbf{Multimodal Processing}: The capability to analyze text and image inputs, such as payment receipts and medical prescriptions.
    \item \textbf{Human-in-the-Loop Escalation}: A confidence-scoring engine that automatically routes complex or sensitive queries with a confidence score below 0.7 to specialized human agents.
    \item \textbf{Staff and Analytics Dashboards}: Dedicated interfaces for real-time ticket handling, knowledge base updates, and performance monitoring of KPIs such as escalation rates and query volume.
    \item \textbf{Agentic RAG Engine}: Utilizing models such as \textbf{Llama 3.2} and \textbf{OpenAI GPT-5}, the backend incorporates a self-validation pipeline to minimize hallucinations and ensure factual grounding.
\end{itemize}

This project establishes a scalable, transparent, and inclusive digital gateway that empowers stakeholders through localized AI innovation. The system not only enhances operational efficiency but also fosters trust and accessibility for a diverse user base, setting a precedent for AI-driven solutions in the non-profit sector of Pakistan.

% The following are automatically populated by LaTeX \chapter, \section and related, \figure, and \table.
\tableofcontents
\listoffigures
\listoftables

\chapter{Introduction}
\label{chap:intro}
\input{chapters/introduction}

\chapter{Literature Review}
\label{chap:lit}
\input{chapters/review}

\chapter{Software Requirement Specification (SRS)}
\label{chap:srs}
\input{chapters/srs}

\chapter{Software Design Specification (SDS)}
\label{chap:sds}
\input{chapters/sds}

\chapter{Methodology, Experiments and Results}
\label{chap:results}
\input{chapters/results}

\chapter{Conclusion and Future Work}
\label{chap:outro}
\input{chapters/conclusion}

\chapter{Reflection}
\label{chap:Reflection}
\input{chapters/reflection}

% \begin{appendices}

% \titleformat{\chapter}[hang]{\bf\huge}{Appendix \thechapter.}{2pc}{}
  
% % This appendix is optional.
% \chapter{More Math}
% \input{chapters/appendix-math}

% % This appendix is required if the data set is not fully described in the main text.
% \chapter{Data}
% \input{chapters/appendix-data}

% % This appendix is required if the code is not fully described in the main text.
% \chapter{Code}
% \input{chapters/appendix-code}
% \end{appendices}

% Print the bibliography using biblatex and include it in the TOC.
\clearpage
\printbibliography[heading=bibintoc,title=References]

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
