\section{System Architecture: Agentic RAG and Frontend Integration}
The system is a full-stack implementation comprising a React-based frontend, a FastAPI backend, and an Agentic Retrieval-Augmented Generation (RAG) reasoning engine powered by Llama 3.2. The architecture is designed to optimize retrieval efficiency, minimize hallucinations, and support multilingual, multimodal interaction.

\subsection{Frontend Architecture and User Interface}
The frontend is built using \textbf{React.js 18}, \textbf{Vite}, and \textbf{Tailwind CSS}, delivering a responsive, chat-based interface. Key features include:
\begin{itemize}
    \item \textbf{Multilingual Interface:} Supports English, Urdu (Nastaliq), and Roman Urdu with seamless switching.
    \item \textbf{Role-Based Dashboards:} Separate interfaces for Users (OTP-based login), Human Agents (ticket handling), and Admins (analytics and monitoring).
    \item \textbf{Real-time Communication:} WebSocket-based messaging enables instant interaction during escalated sessions.
    \item \textbf{Multimodal Input:} OCR pipeline using \textbf{Tesseract} and \textbf{PaddleOCR} processes PNG, JPG, and PDF uploads for text extraction and query grounding.
\end{itemize}

\subsection{Agentic RAG Reasoning Engine}
The backend implements an Agentic AI architecture to regulate retrieval and enforce factual grounding. The system consists of the following components:

\begin{itemize}
    \item \textbf{Router Agent:} Performs retrieval necessity checks to bypass embedding generation for non-informational queries (e.g., greetings), reducing computational overhead by 30--60\%.
    
    \item \textbf{Retriever Agent with Fallback:} Uses \textbf{multilingual-e5-base} embeddings for semantic search. If fewer than two documents exceed a similarity threshold of $\ge 0.6$, a general-domain fallback is triggered to ensure adequate context coverage.
    
    \item \textbf{Evidence Coverage Agent:} Decomposes generated responses into atomic claims and verifies each against retrieved documents. Unsupported claims are removed to prevent hallucinations.
    
    \item \textbf{Self-RAG Critic:} Implements a six-stage validation pipeline: Domain Relevance, Retrieval Necessity, Document Relevance, Answer-in-Context Verification, Support Validation, and Utility Evaluation.
\end{itemize}

\section{Experimental Setup}
The system was evaluated using both a structured query dataset and a defined technical environment.

We are currently testing our chatbot system across nine key modules to ensure overall reliability and performance. This includes validating the RAG (Retrieval-Augmented Generation) pipeline to confirm it is functioning correctly end-to-end, along with thorough testing of all API endpoints for stability and error handling. We are evaluating multimodal and language processing capabilities to ensure the system can handle diverse inputs effectively. Security and privacy checks are being conducted to safeguard user data, while human-in-the-loop mechanisms are assessed for confidence scoring and appropriate escalation. Additionally, we are verifying routing logic to ensure queries are directed correctly, performing deployment and load testing to measure scalability and robustness, running a deep evaluation suite to assess RAG response quality, ensuring database integrity and recovery mechanisms, and conducting full end-to-end frontend testing to validate a seamless user experience.

\subsection{Dataset}
A total of 192 queries were used (64 each in English, Urdu, and Roman Urdu), spanning key domains including Healthcare, Donors, and General NGO services.

\subsection{Technical Configuration}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Component} & \textbf{Specification} \\ \hline
Base LLM & OpenAI GPT-5 \\ \hline
Backup LLM (English \& Roman Urdu) & Llama-3.2-3B-Instruct (GGUF Quantized) \\ \hline
Backup LLM (Urdu) & Alif-1.0-8B-Instruct \cite{alif_instruct_2024} \\ \hline
Embeddings & intfloat/multilingual-e5-base (768-dim) \\ \hline
Vector Store & Supabase pgvector \\ \hline
Knowledge Base & 12+ NGO Domains (PDF, DOCX, TXT) \\ \hline
\end{tabular}
\caption{Experimental Environment Specifications}
\end{table}

\section{Results and Performance Analysis}

\subsection{RAG Evaluation Metrics}
Evaluation was conducted using the \textbf{Deepeval} framework, focusing on:
\begin{itemize}
    \item \textbf{Answer Relevancy:} Degree to which responses remain aligned with the query.
    \item \textbf{Faithfulness:} Extent to which responses are grounded in retrieved context.
    \item \textbf{Contextual Precision and Recall:} Quality and completeness of retrieved documents.
\end{itemize}

\subsection{Accuracy and Hallucination Control}
The integration of \textbf{Self-RAG} and the \textbf{Evidence Coverage Agent} resulted in an increased factual accuracy. The system reduces hallucinations by enforcing claim-level verification and rejecting unsupported outputs.

\subsection{Confidence Scoring and Escalation}
A composite \textbf{Confidence Scoring Engine} aggregates retrieval similarity, token probability, and Self-RAG validation signals.
\begin{itemize}
    \item \textbf{Escalation Threshold:} Queries with confidence scores below $0.70$ are routed to human agents.
    \item \textbf{Outcome:} This mechanism ensures reliable fallback handling for low-certainty or ambiguous queries.
\end{itemize}

\subsection{Latency and Optimization}
\begin{itemize}
    \item \textbf{Embedding Cache:} Semantic deduplication with a 95\% similarity threshold reduces repeated computation, saving 0.5--1.0 seconds per query.
    \item \textbf{Response Time:} End-to-end latency ranges from 30 to 60 seconds depending on query complexity and dialogue depth.
\end{itemize}

\subsection{Multilingual and Multimodal Performance}
\begin{itemize}
    \item \textbf{Multilingual Handling:} Queries in Roman Urdu are translated into English for retrieval, maintaining consistent semantic search performance.
    \item \textbf{Brand Term Protection:} Ensures proper nouns remain unchanged during translation.
    \item \textbf{Multimodal Results:} The OCR-VLM hybrid pipeline achieved a 24.5\% F1-score improvement over image-only processing for structured documents such as medical receipts.
\end{itemize}
